### 2008-08-21 doc/a-rex/arex_tech_doc.tex
Extending BES/A-REX states table to include Deleted and Finished states
Fixes for A-REX document implementing some of Gabor's comments

%% LyX 1.4.5.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twoside,english]{article}
\usepackage{pslatex}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\usepackage{array}
\usepackage{amsmath}
\usepackage{setspace}
\onehalfspacing
\usepackage{amssymb}
\IfFileExists{url.sty}{\usepackage{url}}
                      {\newcommand{\url}{\texttt}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{multirow}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {A.Konstantinov},
  pdftitle = {The NorduGrid Grid Manager and GridFTP Server.},
  pdfsubject = {},
  pdfkeywords = {},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%

@@

Each job gets a directory on the CE called the \emph{session directory}
(SD). Input files are gathered in the SD. The job is supposed to produce
new data files in the SD as well. The A-REX does not guarantee the
availability of any other places accessible by the job other than
SD (unless such a place is part of a requested Runtime Environment).
The SD is also the only place which is controlled by the A-REX. It
is accessible by the user from outside through the HTTP(S) protocol.
Any file created outside the SD is not controlled by the A-REX. Any
exchange of data between client and A-REX (including also program
modules) is performed via HTTP(S). A URL for accessing input/output
files is  obtained through the WS Local Information Description Interface
(LIDI) of A-REX.

@@

\begin{tabular}{|c|c|>{\raggedright}p{10cm}|}
\hline 
Applicable BES State&
ARC Sub-state&
\multicolumn{1}{c|}{Description}\tabularnewline
\hline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{2}{2cm}{Pending}&
Accepting&
Job is in the process of being submitted\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Accepted&
Job was submitted\tabularnewline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{7}{2cm}{Running}&
Preparing&
Stage-in process is going on\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Prepared&
Stage-in process has finished\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Submiting&
Communication with local batch system is in process\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Executing&
Job is being executed in local batch system\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Killing&
Communication with local batch system to terminate execution is in
process\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Executed&
Job execution in local batch system has finished\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Finishing&
Stage-out process is going on\tabularnewline
\hline 
Cancelled&
Failed&
There was a failure during execution\tabularnewline
\cline{1-1} 
Failed&
\multicolumn{1}{c|}{}&
\multicolumn{1}{l|}{}\tabularnewline
\hline 
All&
Pending&
Job is prevented from going to the next state due to some internal
limits; this sub-state appears in parallel with other sub-states\tabularnewline
\hline 
All&
Held&
Job processing is suspended on client request; this sub-state appears
in parallel with other sub-states. This state is reserved for future
and i snot implemented yet.\tabularnewline
\hline
\end{tabular}
\end{table}

@@

\begin{lyxlist}{00.00.0000}
\item [{Filename}] - name of the data file on the executing node.
\item [{\emph{Source}}] - source where the file will be taken from before
execution.
\item [{\emph{Target}}] \emph{-} destination the file will be delivered
to after execution.
\end{lyxlist}
\item [{\emph{Input}\ (POSIX,HPC)}] - file to be used as standard input
for the executable.
\item [{\emph{Output}\ (POSIX,HPC)}] - file to be used as standard output
for the executable.
\item [{\emph{Error}\ (POSIX,HPC)}] - file to be used as standard error
for the executable.
\item [{\emph{MemoryLimit}\ (POSIX)}] - amount of physical memory needed
for execution.
\item [{\emph{TotalPhysicalMemory}}] - same as MemoryLimit.
\item [{\emph{IndividualPhysicalMemory}}] - same as MemoryLimit.
\item [{\emph{CPUTimeLimit}\ (POSIX)}] - maximal amount of CPU time needed
for execution.
\item [{\emph{TotalCPUTime}}] - same as CPUTimeLimit.
\item [{\emph{IndividualCPUTime}}] - same as CPUTimeLimit.
\item [{\emph{WallTimeLimit}\ (POSIX)}] - amount of clock time needed
for execution.
\item [{\emph{TotalCPUCount}}] \emph{-} number of CPUs needed for execution.
\item [{\emph{IndividualCPUCount}}] - same as 6.
\item [{\emph{Environment}\ (POSIX)}] - environment variable.
\end{lyxlist}

@@

\begin{itemize}
\item \textit{libarex.so} - The main module providing main functionality
and web interface. It is implemented as HTTP and SOAP service inside
HED. It is responsible for processing jobs, moving them through states
and running other modules.
\item \textit{downloader} - This is a module responsible for gathering input
files in the SD. It processes the \textit{job.ID.input} file and updates
it.
\item \textit{uploader} - This module is responsible for delivering output
files to the specified SEs and registration at an Indexing Service
(like RLS) as needed. It processes and updates the \textit{job.ID.output}
file.
\item \emph{cache-register} - Utility to register cached data into an Indexing
Service. It reads and modifies cache informational files \emph{old}
and \emph{new} (as described in section \ref{sec:cache}). Configuration
is read directly from the A-REX's configuration file (see section
\ref{SubSection: ConfigFile}). It is run by the A-REX every 5 minutes.
\item \emph{frontend-info-collector} - Utility to gather information about
the frontend. It puts collected information into the \emph{job.ID.diag}
file.
\item \emph{gm-kick} - Sends a signal to the A-REX though a FIFO file to
wake it up. It's used to increase responsiveness of A-REX.
\item \emph{cluster+qju.pl} - Collects and generates information about computing
resource as XML document in NorduGrid and Glue 2 format.
\end{itemize}
The following modules are always run under the Unix account to which
a Grid user is mapped.

\begin{itemize}
\item \textit{smtp-send.sh} and \textit{smtp-send} - These are the modules
responsible for sending e-mail notifications to the user. The format
of the mail messages can be easily changed by editing the simple shell
script \textit{smtp-send.sh}. 
\item \textit{submit-{*}-job} - Here {*} stands for the name of the LRMS.
Currently supported LRMS are PBS/Torque, Condor and SGE. Also \emph{fork}
pseudo-LRMS is supported for testing purposes. This module is responsible
for job submission to the LRMS.
\item \textit{cancel-{*}-job} - This script is for canceling jobs which
have been already submitted to the LRMS.
\item \textit{scan-{*}-job} -This shell script is responsible for notifying
the A-REX about completion of jobs. It's implementation for PBS uses
server logs to extract information about jobs. If logs are not available
it uses the less reliable \emph{qstat} command for that. Other backends
use different techniques.
\end{itemize}
In addition, there is also an administration utility:

\begin{itemize}
\item \textit{gm-jobs} - prints a list of jobs available on the cluster
and the number of jobs in each state.\\
\hspace*{0.5cm}gm-jobs {[}-h] {[}-l] {[}-u uid] {[}-U name]\\
\hspace*{0.5cm}-l -- print more information about each job,\\
\hspace*{0.5cm}-u -- pretend utility is run by user with id \emph{uid},\\
\hspace*{0.5cm}-U -- pretend utility is run by user with name \emph{name}.
\end{itemize}

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} - specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} - specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{session}}\textit{=path} - specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used - \textit{\$HOME/.jobs} . In new configuration file this command
is called \textbf{\textit{sessiondir}}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
the directory to store cached data. Empty \emph{path} disables caching.
Default is not to cache data. Optional \textit{link\_path} specifies
the path at which cache is accessible at computing nodes. If \textit{link\_path}
is set to '.' files are not soft-linked, but copied to session directory.
\item \textbf{\textit{privatecache}}\textit{=path {[}link\_path]} - same
as \textit{cache} command, but cache belongs (owned) to user. For
shared caches use 'cache'.
\item \textbf{\textit{cachedata}}\textit{=path} - allows to specify separate
place to store cache files containing data itself. This can be useful
in case of big data storage available only on NSF server which does
not support file locking. If command or \textit{path} is missing -
default is to store data at place specified in \textit{cache} or \textit{privatecache}
command, together with control files. 
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low water-mark for space used by cache. Values are specified
in bytes. Both \textit{high\_mark} and \textit{low\_mark} can be negative
values. In that case corresponding positive value means space left
on file system. If \textit{low\_mark} is omitted it becomes equal
to \textit{high\_mark}. By default this feature is turned off. To
turn it off explicitly \textit{cachesize} without parameters should
be specified. If turned off cache will grow up till it fills whole
file system.
\item \textbf{\textit{maxrerun}}\textit{=number} - specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}
All per-user commands should be put before \textit{control} command
which initiates serviced user.

@@

\textbf{\textit{RUNTIME\_FRONTEND\_SEES\_NODE}} - if defined should
contain path corresponding to \textit{RUNTIME\_LOCAL\_SCRATCH\_DIR}
as seen on \textbf{frontend} machine. Corresponds to \emph{shared\_scratch}
configuration command.

@@

Figures \ref{fig:no node scratch},\ref{fig:node scratch, not vis on front},\ref{fig:node scratch, vis on front}
present some possible combinations for RUNTIME\_LOCAL\_SCRATCH\_DIR
and RUNTIME\_FRONTEND\_SEES\_NODE and explain how data movement is
performed. Pictures a) correspond to the situation right after all
input files have been gathered in the session directory and show the
actions taken right after the job's script starts. Pictures b) show
the situation while the job is running and the actions which are taken
right after it has finished. Pictures c) illustrate the final situation,
when the job's output files are ready to be uploaded to an external
storage element or be downloaded by the user.

@@

\begin{itemize}
\item joboption\_directory - session directory.
\item joboption\_args - command to be executed as specified in the JD.
\item joboption\_env\_\# - array of 'NAME=VALUE' environment variables (\textbf{not}
bash array).
\item joboption\_runtime\_\# - array of requested \emph{runtimeenvironment}
names (\textbf{not} bash array).
\item joboption\_num - \emph{runtimeenvironment} currently beeing processed
(number starting from 0).
\item joboption\_stdin - name of file to be attached to stdin handle.
\item joboption\_stdout - same for stdout.
\item joboption\_stderr - same for stderr.
\item joboption\_maxcputime - amount of CPU time requested (minutes).
\item joboption\_maxmemory - amount of memory requested (megabytes).
\item joboption\_count - number of processors requested.
\item joboption\_lrms - LRMS to be used to run job.
\item joboption\_queue - name of a queue of LRMS to put job into.
\item joboption\_nodeproperty\_\# - array of properties of computing nodes
(LRMS specific, \textbf{not} bash array).
\item joboption\_jobname - name of the job as given by user.
\item joboption\_rsl - whole RSL for very clever submission scripts.
\item joboption\_rsl\_\emph{name} - RSL attributes and values (like joboption\_rsl\_executable=''/bin/echo'')
\end{itemize}
For example \emph{joboption\_args} could be changed to wrap main executable.
Or \emph{joboption\_runtime} could be expanded if current one depends
on others.

@@

The A-REX service is a plugable module of the HED. So first You need
to setup your HED - see HED documentation.

@@

\section*{Appendix A. Session directory access through HTTP(S) interface}

@@

\section*{Appendix B. Configuration schema of A-REX}

@@

\section*{Appendix C. A-REX WSDL}

@@

\section*{Appendix D. Delegation WSDL}

@@

\section*{Appendix E. ARC extensions for JSDL schema}

@@

\section*{Appendix F. Error messages of A-REX}

If job has not finished successfully the A-REX puts one or more lines
into \textit{job.ID.failed}. Possible values include those generated
by the A-REX itself:

\begin{tabular}{|p{2.5in}|p{4in}|}
\hline 
\emph{Error string}&
\emph{Reason/description}\tabularnewline
\hline 
Internal error&
Error in internal algorithm\tabularnewline
\hline 
Internal error: can't read local file&
Error manipulating files in the control directory\tabularnewline
\hline 
Failed reading local job information&
-//-\tabularnewline
\hline 
Failed reading status of the job&
-//-\tabularnewline
\hline 
Failed writing job status&
-//-\tabularnewline
\hline 
Failed during processing failure&
-//-\tabularnewline
\hline 
Serious troubles (problems during processing problems)&
-//-\tabularnewline
\hline 
Failed initiating job submission to LRMS&
Could not run backend executable to pass job to LRMS\tabularnewline
\hline 
Job submission to LRMS failed&
Backend executable supposed to pass job to LRMs returned non-zero
exit code\tabularnewline
\hline 
Failed extracting LRMS ID due to some internal error&
Output of Backend executable supposed to contain local ID of passed
job could not be parsed\tabularnewline
\hline 
Failed in files upload (post-processing)&
Failed to upload some or all output files\tabularnewline
\hline 
Failed in files upload due to expired credentials - try to renew&
Failed to upload some or all output files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run uploader (post-processing)&
Could not run \emph{uploader} executable\tabularnewline
\hline 
uploader failed (postprocessing)&
Generic error related to \emph{uploader} component\tabularnewline
\hline 
Failed in files download (pre-processing)&
Failed to upload some or all input files\tabularnewline
\hline 
Failed in files download due to expired credentials - try to renew&
Failed to download some or all input files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run downloader (pre-processing)&
Could not run \emph{downloader} executable\tabularnewline
\hline
downloader failed (preprocessing)&
Generic error related to \emph{downloader} component\tabularnewline
\hline
User requested to cancel the job&
A-REX detected external request to cancel this job, most probably
issued by user\tabularnewline
\hline
Could not process RSL&
Job description could not be processed to syntax errors or missing
elements\tabularnewline
\hline
User requested dryrun. Job skiped.&
Job description contains request not to process this job\tabularnewline
\hline
LRMS error: (CODE) DESCRIPTION&
LRMS returned error. CODE is replaced with numeric code of LRMS, and
DESCRIPTION with textual description\tabularnewline
\hline
Plugin at state STATE failed: OUTPUT&
External plugin specified in A-REX configuration returned non-zero
exit code. STATE is replcaced by name of state to which job was going
to be passed, OUTPUT by textual output generated by plugin.\tabularnewline
\hline
Failed running plugin at state STATE&
External plugin specified in A-REX configuration could not be executed.\tabularnewline
\hline
\end{tabular}

\medskip{}
Provided by downloader component (URL is replcaced by source of input
file, FILE by name of file):

>>>>

%% LyX 1.4.5.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twoside,english]{article}
\usepackage{pslatex}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{setspace}
\onehalfspacing
\usepackage{amssymb}
\IfFileExists{url.sty}{\usepackage{url}}
                      {\newcommand{\url}{\texttt}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{multirow}
\usepackage{verbatim}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {A.Konstantinov},
  pdftitle = {The NorduGrid Grid Manager and GridFTP Server.},
  pdfsubject = {},
  pdfkeywords = {},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%

@@

Each job gets a directory on the CE called the \emph{session directory}
(SD). Input files are gathered in the SD. The job is supposed to produce
new data files in the SD as well. The A-REX does not guarantee the
availability of any other places accessible by the job other than
SD (unless such a place is part of a requested Runtime Environment).
The SD is also the only place which is controlled by the A-REX. It
is accessible by the user from outside through the HTTP(S) protocol.
Any file created outside the SD is not controlled by the A-REX. Any
exchange of data between client and A-REX (including also program
modules) is performed via HTTP(S). An URL for accessing input/output
files is  obtained through the WS Local Information Description Interface
(LIDI) of A-REX.

@@

\begin{tabular}{|c|c|>{\raggedright}p{10cm}|}
\hline 
Applicable BES State&
ARC Sub-state&
\multicolumn{1}{c|}{Description}\tabularnewline
\hline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{2}{2cm}{Pending}&
Accepting&
Job is in the process of being submitted\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Accepted&
Job was submitted\tabularnewline
\hline 
\renewcommand{\multirowsetup}{\centering}\multirow{7}{2cm}{Running}&
Preparing&
Stage-in process is going on\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Prepared&
Stage-in process has finished\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Submiting&
Communication with local batch system is in process\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Executing&
Job is being executed in local batch system\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Killing&
Communication with local batch system to terminate execution is in
process\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Executed&
Job execution in local batch system has finished\tabularnewline
\cline{2-2} \cline{3-3} 
\multicolumn{1}{|c|}{}&
Finishing&
Stage-out process is going on\tabularnewline
\hline 
Cancelled&
Finished&
There was a failure during execution\tabularnewline
\cline{1-1} 
Failed&
\multicolumn{1}{c|}{}&
\multicolumn{1}{l|}{}\tabularnewline
\hline 
Finished&
Finished&
Job finished successfully\tabularnewline
\hline 
Finished&
Deleted&
Job finished and was left in A-REX too long\tabularnewline
\hline 
All&
Pending&
Job is prevented from going to the next state due to some internal
limits; this sub-state appears in parallel with other sub-states\tabularnewline
\hline 
All&
Held&
Job processing is suspended on client request; this sub-state appears
in parallel with other sub-states. This state is reserved for future
and i snot implemented yet.\tabularnewline
\hline
\end{tabular}
\end{table}

@@

\begin{lyxlist}{00.00.0000}
\item [{Filename}] - name of the data file on the executing node.
\item [{\emph{Source}}] - source where the file will be taken from before
execution.
\item [{\emph{Target}}] \emph{-} destination the file will be delivered
to after execution.
\end{lyxlist}
\item [{\emph{Input}\ (POSIX,HPC)}] - file to be used as standard input
for the executable.
\item [{\emph{Output}\ (POSIX,HPC)}] - file to be used as standard output
for the executable.
\item [{\emph{Error}\ (POSIX,HPC)}] - file to be used as standard error
for the executable.
\item [{\emph{MemoryLimit}\ (POSIX)}] - amount of physical memory needed
for execution.
\item [{\emph{TotalPhysicalMemory}}] - same as MemoryLimit.
\item [{\emph{IndividualPhysicalMemory}}] - same as MemoryLimit.
\item [{\emph{CPUTimeLimit}\ (POSIX)}] - maximal amount of CPU time needed
for execution.
\item [{\emph{TotalCPUTime}}] - same as CPUTimeLimit.
\item [{\emph{IndividualCPUTime}}] - same as CPUTimeLimit.
\item [{\emph{WallTimeLimit}\ (POSIX)}] - amount of clock time needed
for execution.
\item [{\emph{TotalCPUCount}}] \emph{-} number of CPUs needed for execution.
\item [{\emph{IndividualCPUCount}}] - same as \emph{TotalCPUCount}.
\end{lyxlist}
%Environment(POSIX) - environment variable.

@@

\begin{itemize}
\item \textit{libarex.so} - The main module providing main functionality
and web interface. It is implemented as HTTP and SOAP service inside
HED. It is responsible for processing jobs, moving them through states
and running other modules.
\item \textit{downloader} - This is a module responsible for gathering input
files in the SD. It processes the \textit{job.ID.input} file and updates
it.
\item \textit{uploader} - This module is responsible for delivering output
files to the specified SEs and registration at an Indexing Service
(like RLS) as needed. It processes and updates the \textit{job.ID.output}
file.
\end{itemize}
%cache-register - Utility to register cached data into an Indexing Service. It reads and modifies cache informational files old and new (as described in section ). Configuration is read directly from the A-REX's configuration file (see section ). It is run by the A-REX every 5 minutes.

%frontend-info-collector - Utility to gather information about the frontend. It puts collected information into the job.ID.diag file.

\begin{itemize}
\item \emph{gm-kick} - Sends a signal to the A-REX though a FIFO file to
wake it up. It's used to increase responsiveness of A-REX.
\item \emph{cluster+qju.pl} - Collects and generates information about computing
resource as XML document in NorduGrid and Glue 2 format.
\end{itemize}
The following modules are always run under the Unix account to which
a Grid user is mapped.

\begin{itemize}
\item \textit{smtp-send.sh} and \textit{smtp-send} - These are the modules
responsible for sending e-mail notifications to the user. The format
of the mail messages can be easily changed by editing the simple shell
script \textit{smtp-send.sh}. 
\item \textit{submit-{*}-job} - Here {*} stands for the name of the LRMS.
Currently supported LRMS are PBS/Torque, Condor and SGE. Also \emph{fork}
pseudo-LRMS is supported for testing purposes. This module is responsible
for job submission to the LRMS.
\item \textit{cancel-{*}-job} - This script is for canceling jobs which
have been already submitted to the LRMS.
\item \textit{scan-{*}-job} -This shell script is responsible for notifying
the A-REX about completion of jobs. It's implementation for PBS uses
server logs to extract information about jobs. If logs are not available
it uses the less reliable \emph{qstat} command for that. Other backends
use different techniques.
\end{itemize}
\begin{comment}In addition, there is also an administration utility:

\begin{itemize}
\item \textit{gm-jobs} - prints a list of jobs available on the cluster
and the number of jobs in each state.\\
\hspace*{0.5cm}gm-jobs {[}-h] {[}-l] {[}-u uid] {[}-U name]\\
\hspace*{0.5cm}-l -- print more information about each job,\\
\hspace*{0.5cm}-u -- pretend utility is run by user with id \emph{uid},\\
\hspace*{0.5cm}-U -- pretend utility is run by user with name \emph{name}.
\end{itemize}
\end{comment}

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} - specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} - specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{session}}\textit{=path} - specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used - \textit{\$HOME/.jobs} . In new configuration file this command
is called \textbf{\textit{sessiondir}}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
the directory to store cached data. Empty \emph{path} disables caching.
Default is not to cache data. Optional \textit{link\_path} specifies
the path at which cache is accessible at computing nodes. If \textit{link\_path}
is set to '.' files are not soft-linked, but copied to session directory.
\item \textbf{\textit{privatecache}}\textit{=path {[}link\_path]} - same
as \textit{cache} command, but cache belongs (owned) to user. For
shared caches use 'cache'.
\item \textbf{\textit{cachedata}}\textit{=path} - allows to specify separate
place to store cache files containing data itself. This can be useful
in case of big data storage available only on NFS server which does
not support file locking. If command or \textit{path} is missing -
default is to store data at place specified in \textit{cache} or \textit{privatecache}
command, together with control files. 
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low water-mark for space used by cache. Values are specified
in bytes. Both \textit{high\_mark} and \textit{low\_mark} can be negative
values. In that case corresponding positive value means space left
on file system. If \textit{low\_mark} is omitted it becomes equal
to \textit{high\_mark}. By default this feature is turned off. To
turn it off explicitly \textit{cachesize} without parameters should
be specified. If turned off cache will grow up till it fills whole
file system.
\item \textbf{\textit{maxrerun}}\textit{=number} - specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}
All per-user commands should be put before \textit{control} command
which initiates serviced user.

@@

\textbf{\textit{RUNTIME\_FRONTEND\_SEES\_NODE}} - if defined should
contain path corresponding to \textit{}\\
\textit{RUNTIME\_LOCAL\_SCRATCH\_DIR} as seen on \textbf{frontend}
machine. Corresponds to \emph{shared\_scratch} configuration command.

@@

Figures \ref{fig:no node scratch},\ref{fig:node scratch, not vis on front},\ref{fig:node scratch, vis on front}
present some possible combinations for RUNTIME\_LOCAL\_SCRATCH\_DIR
and \\
RUNTIME\_FRONTEND\_SEES\_NODE and explain how data movement is performed.
Pictures a) correspond to the situation right after all input files
have been gathered in the session directory and show the actions taken
right after the job's script starts. Pictures b) show the situation
while the job is running and the actions which are taken right after
it has finished. Pictures c) illustrate the final situation, when
the job's output files are ready to be uploaded to an external storage
element or be downloaded by the user.

@@

\begin{itemize}
\item joboption\_directory - session directory.
\item joboption\_arg\_\# - command with arguments to be executed as specified
in the JD (\textbf{not} bash array).
\item joboption\_env\_\# - array of 'NAME=VALUE' environment variables (\textbf{not}
bash array).
\item joboption\_runtime\_\# - array of requested \emph{runtimeenvironment}
names (\textbf{not} bash array).
\item joboption\_num - \emph{runtimeenvironment} currently beeing processed
(number starting from 0).
\item joboption\_stdin - name of file to be attached to stdin handle.
\item joboption\_stdout - same for stdout.
\item joboption\_stderr - same for stderr.
\item joboption\_maxcputime - amount of CPU time requested (minutes).
\item joboption\_maxmemory - amount of memory requested (megabytes).
\item joboption\_count - number of processors requested.
\item joboption\_lrms - LRMS to be used to run job.
\item joboption\_queue - name of a queue of LRMS to put job into.
\item joboption\_nodeproperty\_\# - array of properties of computing nodes
(LRMS specific, \textbf{not} bash array).
\item joboption\_jobname - name of the job as given by user.
\item joboption\_rsl - whole RSL for very clever submission scripts.
\item joboption\_rsl\_\emph{name} - RSL attributes and values (like joboption\_rsl\_executable=''/bin/echo'')
\end{itemize}
For example \emph{joboption\_arg\_\#} could be changed to wrap main
executable. Or \emph{joboption\_runtime} could be expanded if current
one depends on others.

@@

The A-REX service is a pluggable module of the HED. So first You need
to setup your HED - see HED documentation.

@@

\appendix

\section{Session directory access through HTTP(S) interface}

@@

\section{Configuration schema of A-REX}

@@

\section{A-REX WSDL}

@@

\section{Delegation WSDL}

@@

\section{ARC extensions for JSDL schema}

@@

\section{Error messages of A-REX}

If job has not finished successfully the A-REX puts one or more lines
into \textit{job.ID.failed}. Possible values include those generated
by the A-REX itself:\\
\begin{longtable}{|p{2.5in}|p{4in}|}
\hline 
\emph{Error string}&
\emph{Reason/description}\tabularnewline
\hline 
Internal error&
Error in internal algorithm\tabularnewline
\hline 
Internal error: can't read local file&
Error manipulating files in the control directory\tabularnewline
\hline 
Failed reading local job information&
-//-\tabularnewline
\hline 
Failed reading status of the job&
-//-\tabularnewline
\hline 
Failed writing job status&
-//-\tabularnewline
\hline 
Failed during processing failure&
-//-\tabularnewline
\hline 
Serious troubles (problems during processing problems)&
-//-\tabularnewline
\hline 
Failed initiating job submission to LRMS&
Could not run backend executable to pass job to LRMS\tabularnewline
\hline 
Job submission to LRMS failed&
Backend executable supposed to pass job to LRMS returned non-zero
exit code\tabularnewline
\hline 
Failed extracting LRMS ID due to some internal error&
Output of Backend executable supposed to contain local ID of passed
job could not be parsed\tabularnewline
\hline 
Failed in files upload (post-processing)&
Failed to upload some or all output files\tabularnewline
\hline 
Failed in files upload due to expired credentials - try to renew&
Failed to upload some or all output files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run uploader (post-processing)&
Could not run \emph{uploader} executable\tabularnewline
\hline 
uploader failed (postprocessing)&
Generic error related to \emph{uploader} component\tabularnewline
\hline 
Failed in files download (pre-processing)&
Failed to upload some or all input files\tabularnewline
\hline 
Failed in files download due to expired credentials - try to renew&
Failed to download some or all input files most probably due to expired
credentials (proxy certificate)\tabularnewline
\hline 
Failed to run downloader (pre-processing)&
Could not run \emph{downloader} executable\tabularnewline
\hline
downloader failed (preprocessing)&
Generic error related to \emph{downloader} component\tabularnewline
\hline
User requested to cancel the job&
A-REX detected external request to cancel this job, most probably
issued by user\tabularnewline
\hline
Could not process RSL&
Job description could not be processed to syntax errors or missing
elements\tabularnewline
\hline
User requested dryrun. Job skiped.&
Job description contains request not to process this job\tabularnewline
\hline
LRMS error: (CODE) DESCRIPTION&
LRMS returned error. CODE is replaced with numeric code of LRMS, and
DESCRIPTION with textual description\tabularnewline
\hline
Plugin at state STATE failed: OUTPUT&
External plugin specified in A-REX configuration returned non-zero
exit code. STATE is replcaced by name of state to which job was going
to be passed, OUTPUT by textual output generated by plugin.\tabularnewline
\hline
Failed running plugin at state STATE&
External plugin specified in A-REX configuration could not be executed.\tabularnewline
\hline
\end{longtable}
